Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-09-24 paper-v1.tex
cleanup

Access management of the Ants-Review protocol is defined and controlled by \emph{AntsReviewRoles} (see Figure \ref{fig:contracts} (\textbf{b})), implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Library\footnote[10]{\emph{OpenZeppelin Library}.\textsc{URL:}https://openzeppelin.com.} that is used to define the Issuer and Peer-Reviewer Roles. AntsReviewRoles also integrates a circuit breaker design pattern via \emph{Pausable.sol} by OpenZeppelin to allow the Pauser Role, granted by default to the owner of the smart contracts, to pause (or unpause) all the functions in case of a security emergency, such as an attack to the smart contracts.

@@

\paragraph{\textbf{Pseudo-anonymity}.}EOAs in Ethereum are controlled via private keys. However, the privacy is limited by the fact that both the blockchain and its transactions are public.  Therefore, the details of the transactions are visible to anyone by browsing a block explorer (such as Etherscan) and are subject to data mining that could extract value and identify users in the blockchain.
\paragraph{\textbf{Private transactions}.}AZTEC Protocol  was conceived to enable privacy on public blockchains. It uses Zero-Knowledge Succinct Non-Interactive Argument of Knowledge (ZK-SNARKs)\cite{zSNARK} and homomorphic encryption\footnote[11]{\emph{Homomorphic Encryption}. \textsc{URL:}\newline https://vitalik.ca/general/2020/07/20/homomorphic.html.} to validate encrypted transactions. ZK-SNARKs are zero-knowledge proofs that require no interaction between prover and verifier. ZK-SNARKs are used inside the Ants-Review protocol via the zkANTS token to allow private transactions between the agents. Future developments will allow leverage on Permutations over Lagrange-bases for Oecumenical Noninteractive arguments of Knowledge (PLONK) \cite{PLONK} proofs, a universal zkSNARK construction that reduces gas costs and improves scalability.

\subsubsection{Tokenomics}
Ants-Review integrates a few \emph{ERC20}\footnote[12]{\emph{EIP 20}. \textsc{URL:} https://eips.ethereum.org/EIPS/eip-20.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
\newline ANTS (see Figure \ref{fig:contracts}, (\textbf{c})) is the primary protocol token and can be staked into an AntReview. It's implemented by inheriting \emph{ERC20.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
\newline zkANTS (see Figure \ref{fig:contracts}, (\textbf{d})) is a wrapper of ANTS that will be used inside the protocol to allow for private transactions among the agents (issuer and reviewer), preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters. It will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine, \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens. In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[13]{\emph{EIP  1724}.\textsc{URL:}\url{https://github.com/ethereum/EIPs/issues/1724.}} will be used as a template to build an AZTEC-compatible asset.

@@

\section{Discussions}
We have described how Ants-Review protocol can solve the limitations of the current peer-review system (see 2.1). In particular we showed how the lack of recognition, the lack of transparency, fraud and misconduct can be solved via the Ants-Review Protocol (see § AntsReview in 3.2); the social and cognitive biases via anonymity granted by AZTEC Protocol (see § Privacy in 3.2); the slowness of the process, the need for evaluation of the peer-reviews themselves and the need for increasing the number of reviewers through the creation of the community of Anters. 
\subsection{Future developments}
An interesting aspect of the protocol is the double function of an AntReview respectively as a bounty and as a pool to stake ERC20 tokens like Dai\footnote[14]{\emph{Dai}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation.}. Moreover, the duration of peer-reviews consents to connect the protocol to De-Fi services with the possibility for the community to accrue interest over time via MakerDAO Dai Saving Rate (Pot\footnote[16]{\emph{Pot}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/rates-module/pot-detailed-documentation.}) or Compound\footnote[17]{\emph{Compound}.\textsc{URL:}https://compound.finance.}, to cite a few.
Therefore, an ERC20 \emph{pool token} would be automatically released by the protocol, representing the accrued interest on the Anters' stake over time that can be traded, sold, or held as the Anter desires.
A Decentralized Autonomous Organization (DAO) \cite{Wang-DAO,DAOContr} could be formed in the future to allow ANTS stakers to participate in the governance of important aspects of the protocol, from smart contracts upgrades to minor changes in settings across the protocol.
\newline Finally, a protocol upgrade inspired by \emph{Discover} \footnote[18]{\emph{Discover.sol}. \textsc{URL:}\newline https://github.com/dap-ps/discover/blob/master/contracts/Discover.sol.}, a web3 browser by \emph{Status} \footnote[19]{\emph{Status}.\textsc{URL:}https://status.im/.} and still under investigation would allow Anters to validate peer-reviews via an upvote/downvote system that will consent the protocol to automatically pay out the reward to the reviewers based on the votes associated with their peer-reviews.

@@

\subsubsection{Acknowledgements} We would like to thank Matteo A. Tambussi, Andy Tudhope, Mark Beylin, Simona Pop, Evan C. Harris and the external anonymous peer-reviewers for useful comments and revisions; Mitrasish Mukherjee for contributions on the interface.}

>>>>

Access management of the Ants-Review protocol is defined and controlled by \emph{AntsReviewRoles} (see Figure \ref{fig:contracts} (\textbf{b})), implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Library\footnote[10]{\emph{OpenZeppelin Library}.\textsc{URL:} https://openzeppelin.com.} that is used to define the Issuer and Peer-Reviewer Roles. AntsReviewRoles also integrates a circuit breaker design pattern via \emph{Pausable.sol} by OpenZeppelin to allow the Pauser Role, granted by default to the owner of the smart contracts, to pause (or unpause) all the functions in case of a security emergency, such as an attack to the smart contracts.

@@

\paragraph{\textbf{Pseudo-anonymity}.}EOAs in Ethereum are controlled via private keys. However, the privacy is limited by the fact that both the blockchain and its transactions are public.  Therefore, the details of the transactions are visible to anyone by browsing a block explorer (such as Etherscan \footnote[11]{\emph{Etherscan}. \textsc{URL:} https://etherscan.io/.}) and are subject to data mining that could extract value and identify users in the blockchain.
\paragraph{\textbf{Private transactions}.}AZTEC Protocol was conceived to enable privacy on public blockchains. It uses Zero-Knowledge Succinct Non-Interactive Argument of Knowledge (ZK-SNARKs)\cite{zSNARK} and homomorphic encryption\footnote[12]{\emph{Homomorphic Encryption}. \textsc{URL:}\newline https://vitalik.ca/general/2020/07/20/homomorphic.html.} to validate encrypted transactions. ZK-SNARKs are zero-knowledge proofs that require no interaction between prover and verifier. ZK-SNARKs are used inside the Ants-Review protocol via the zkANTS token to allow private transactions between the agents. Future developments will allow leverage on Permutations over Lagrange-bases for Oecumenical Noninteractive arguments of Knowledge (PLONK) \cite{PLONK} proofs, a universal zkSNARK construction that reduces gas costs and improves scalability.

\subsubsection{Tokenomics}
Ants-Review integrates a few \emph{ERC20}\footnote[13]{\emph{EIP 20}. \textsc{URL:} https://eips.ethereum.org/EIPS/eip-20.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
\newline ANTS (see Figure \ref{fig:contracts}, (\textbf{c})) is the primary protocol token and can be staked into an AntReview. It's implemented by inheriting \emph{ERC20.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
\newline zkANTS (see Figure \ref{fig:contracts}, (\textbf{d})) is a wrapper of ANTS that will be used inside the protocol to allow for private transactions among the agents (issuer and reviewer), preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters. It will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine, \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens. In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[14]{\emph{EIP  1724}.\textsc{URL:} https://github.com/ethereum/EIPs/issues/1724.} will be used as a template to build an AZTEC-compatible asset.

@@

\section{Discussions}
We have described how Ants-Review protocol can solve the limitations of the current peer-review system (see 2.1). In particular we showed how the lack of recognition, the lack of transparency, fraud and misconduct can be solved via the Ants-Review Protocol (see § AntsReview in 3.2); the social and cognitive biases via anonymity granted by AZTEC Protocol (see § Privacy in 3.2); the slowness of the process, the need for evaluation of the peer-reviews themselves and the need for increasing the number of reviewers through the creation of the community of Anters. 
\subsection{Future developments}
An interesting aspect of the protocol is the double function of an AntReview respectively as a bounty and as a pool to stake ERC20 tokens like Dai\footnote[15]{\emph{Dai}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation.}. Moreover, the duration of peer-reviews consents to connect the protocol to De-Fi services with the possibility for the community to accrue interest over time via MakerDAO Dai Saving Rate (Pot\footnote[16]{\emph{Pot}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/rates-module/pot-detailed-documentation.}) or Compound\footnote[17]{\emph{Compound}.\textsc{URL:} https://compound.finance.}, to cite a few.
Therefore, an ERC20 \emph{pool token} would be automatically released by the protocol, representing the accrued interest on the Anters' stake over time that can be traded, sold, or held as the Anter desires.
A Decentralized Autonomous Organization (DAO) \cite{Wang-DAO,DAOContr} could be formed in the future to allow ANTS stakers to participate in the governance of important aspects of the protocol, from smart contracts upgrades to minor changes in settings across the protocol.
\newline Finally, a protocol upgrade inspired by \emph{Discover} \footnote[18]{\emph{Discover.sol}. \textsc{URL:}\newline https://github.com/dap-ps/discover/blob/master/contracts/Discover.sol.}, a web3 browser by \emph{Status} \footnote[19]{\emph{Status}.\textsc{URL:} https://status.im/.} and still under investigation would allow Anters to validate peer-reviews via an upvote/downvote system that will consent the protocol to automatically pay out the reward to the reviewers based on the votes associated with their peer-reviews.

@@

\subsubsection{Acknowledgements} We would like to thank Matteo A. Tambussi, Andy Tudhope, Mark Beylin, Evan C. Harris and the external anonymous peer-reviewers for useful comments and revisions; Mitrasish Mukherjee for contributions on the interface.}
